\subsection*{Nodes in the documentation tree of the Perl Module output format.}

This is a description of the structure of the documentation tree in {\bf DoxyDocs.pm}. Each item in the list below describes a node in the tree, and the format of the description is as follows:

\begin{itemize}
\item \mbox{[} key =$>$ \mbox{]} {\bf Name} {\em (type)\/}. Explanation of the content. \end{itemize}


Where

\begin{itemize}
\item The \char`\"{}key =\&gt;\char`\"{} part only appears if the parent node is a hash. \char`\"{}key\char`\"{} is the key for this node.

\item {\bf \char`\"{}Name\char`\"{}} is a unique name for the node, defined in DoxyModel.pm.

\item {\em \char`\"{}(type)\char`\"{}\/} is the type of the node: \char`\"{}string\char`\"{} for string nodes, \char`\"{}hash\char`\"{} for hash nodes, \char`\"{}list\char`\"{} for list nodes, and \char`\"{}doc\char`\"{} for documentation subtrees. The structure of documentation subtrees is not described anywhere yet, but you can look for example at {\bf doxylatex.pl} to see how to process it.

\end{itemize}


The meaning of each node in the documentation tree is as follows: \begin{itemize}
\item {\bf Root} {\em (hash)\/}. Root node. \begin{itemize}
\item classes =$>$ {\bf Classes} {\em (list)\/}. Documented classes. \begin{itemize}
\item {\bf Class} {\em (hash)\/}. A documented class. \begin{itemize}
\item protected\_\-members =$>$ {\bf ClassProtectedMembers} {\em (hash)\/}. Information about the protected members in the class. \begin{itemize}
\item members =$>$ {\bf ClassProtectedMemberList} {\em (list)\/}. protected member list. \begin{itemize}
\item {\bf ClassProtectedMember} {\em (hash)\/}. A protected member. \begin{itemize}
\item protection =$>$ {\bf ClassProtectedMemberProtection} {\em (string)\/}. Protection of the protected member. \item detailed =$>$ {\bf ClassProtectedMemberDetailed} {\em (hash)\/}. Detailed information about the protected member. \begin{itemize}
\item doc =$>$ {\bf ClassProtectedMemberDetailedDoc} {\em (doc)\/}. Detailed documentation for the protected member. \item see =$>$ {\bf ClassProtectedMemberSee} {\em (doc)\/}. \char`\"{}See also\char`\"{} documentation for the protected member. \end{itemize}
\item kind =$>$ {\bf ClassProtectedMemberKind} {\em (string)\/}. Kind of protected member (usually \char`\"{}variable\char`\"{}). \item name =$>$ {\bf ClassProtectedMemberName} {\em (string)\/}. Name of the protected member. \item type =$>$ {\bf ClassProtectedMemberType} {\em (string)\/}. Data type of the protected member. \end{itemize}
\end{itemize}
\end{itemize}
\item detailed =$>$ {\bf ClassDetailed} {\em (hash)\/}. Detailed information about the class. \begin{itemize}
\item doc =$>$ {\bf ClassDetailedDoc} {\em (doc)\/}. Detailed documentation block for the class. \end{itemize}
\item protected\_\-typedefs =$>$ {\bf ClassProtectedTypedefs} {\em (hash)\/}. Information about the protected typedefs in the class. \begin{itemize}
\item members =$>$ {\bf ClassProtectedTypedefList} {\em (list)\/}. protected typedef list. \begin{itemize}
\item {\bf ClassProtectedTypedef} {\em (hash)\/}. A protected typedef. \begin{itemize}
\item protection =$>$ {\bf ClassProtectedTypedefProtection} {\em (string)\/}. Protection of the protected typedef. \item detailed =$>$ {\bf ClassProtectedTypedefDetailed} {\em (hash)\/}. Detailed information about the protected typedef. \begin{itemize}
\item doc =$>$ {\bf ClassProtectedTypedefDetailedDoc} {\em (doc)\/}. Detailed documentation for the protected typedef. \item see =$>$ {\bf ClassProtectedTypedefSee} {\em (doc)\/}. \char`\"{}See also\char`\"{} documentation for the protected typedef. \end{itemize}
\item kind =$>$ {\bf ClassProtectedTypedefKind} {\em (string)\/}. Kind of protected typedef (usually \char`\"{}typedef\char`\"{}). \item name =$>$ {\bf ClassProtectedTypedefName} {\em (string)\/}. Name of the protected typedef. \item type =$>$ {\bf ClassProtectedTypedefType} {\em (string)\/}. Data type of the protected typedef. \end{itemize}
\end{itemize}
\end{itemize}
\item name =$>$ {\bf ClassName} {\em (string)\/}. Name of the class. \item private\_\-members =$>$ {\bf ClassPrivateMembers} {\em (hash)\/}. Information about the private members in the class. \begin{itemize}
\item members =$>$ {\bf ClassPrivateMemberList} {\em (list)\/}. private member list. \begin{itemize}
\item {\bf ClassPrivateMember} {\em (hash)\/}. A private member. \begin{itemize}
\item protection =$>$ {\bf ClassPrivateMemberProtection} {\em (string)\/}. Protection of the private member. \item detailed =$>$ {\bf ClassPrivateMemberDetailed} {\em (hash)\/}. Detailed information about the private member. \begin{itemize}
\item doc =$>$ {\bf ClassPrivateMemberDetailedDoc} {\em (doc)\/}. Detailed documentation for the private member. \item see =$>$ {\bf ClassPrivateMemberSee} {\em (doc)\/}. \char`\"{}See also\char`\"{} documentation for the private member. \end{itemize}
\item kind =$>$ {\bf ClassPrivateMemberKind} {\em (string)\/}. Kind of private member (usually \char`\"{}variable\char`\"{}). \item name =$>$ {\bf ClassPrivateMemberName} {\em (string)\/}. Name of the private member. \item type =$>$ {\bf ClassPrivateMemberType} {\em (string)\/}. Data type of the private member. \end{itemize}
\end{itemize}
\end{itemize}
\item private\_\-typedefs =$>$ {\bf ClassPrivateTypedefs} {\em (hash)\/}. Information about the private typedefs in the class. \begin{itemize}
\item members =$>$ {\bf ClassPrivateTypedefList} {\em (list)\/}. private typedef list. \begin{itemize}
\item {\bf ClassPrivateTypedef} {\em (hash)\/}. A private typedef. \begin{itemize}
\item protection =$>$ {\bf ClassPrivateTypedefProtection} {\em (string)\/}. Protection of the private typedef. \item detailed =$>$ {\bf ClassPrivateTypedefDetailed} {\em (hash)\/}. Detailed information about the private typedef. \begin{itemize}
\item doc =$>$ {\bf ClassPrivateTypedefDetailedDoc} {\em (doc)\/}. Detailed documentation for the private typedef. \item see =$>$ {\bf ClassPrivateTypedefSee} {\em (doc)\/}. \char`\"{}See also\char`\"{} documentation for the private typedef. \end{itemize}
\item kind =$>$ {\bf ClassPrivateTypedefKind} {\em (string)\/}. Kind of private typedef (usually \char`\"{}typedef\char`\"{}). \item name =$>$ {\bf ClassPrivateTypedefName} {\em (string)\/}. Name of the private typedef. \item type =$>$ {\bf ClassPrivateTypedefType} {\em (string)\/}. Data type of the private typedef. \end{itemize}
\end{itemize}
\end{itemize}
\item protected\_\-methods =$>$ {\bf ClassProtectedMethods} {\em (hash)\/}. Information about the protected methods in the class. \begin{itemize}
\item members =$>$ {\bf ClassProtectedMethodList} {\em (list)\/}. protected method list. \begin{itemize}
\item {\bf ClassProtectedMethod} {\em (hash)\/}. A protected method. \begin{itemize}
\item parameters =$>$ {\bf ClassProtectedMethodParams} {\em (list)\/}. List of the parameters of the protected method. \begin{itemize}
\item {\bf ClassProtectedMethodParam} {\em (hash)\/}. A parameter of the protected method. \begin{itemize}
\item declaration\_\-name =$>$ {\bf ClassProtectedMethodParamName} {\em (string)\/}. The name of the parameter. \item type =$>$ {\bf ClassProtectedMethodParamType} {\em (string)\/}. The data type of the parameter. \end{itemize}
\end{itemize}
\item protection =$>$ {\bf ClassProtectedMethodProtection} {\em (string)\/}. Protection of the protected method. \item virtualness =$>$ {\bf ClassProtectedMethodVirtualness} {\em (string)\/}. Virtualness of the protected method. \item detailed =$>$ {\bf ClassProtectedMethodDetailed} {\em (hash)\/}. Detailed information about the protected method. \begin{itemize}
\item params =$>$ {\bf ClassProtectedMethodPDBlocks} {\em (list)\/}. List of parameter documentation blocks for the protected method. \begin{itemize}
\item {\bf ClassProtectedMethodPDBlock} {\em (hash)\/}. A parameter documentation block for the protected method. \begin{itemize}
\item parameters =$>$ {\bf ClassProtectedMethodPDParams} {\em (list)\/}. Parameter list for this parameter documentation block. \begin{itemize}
\item {\bf ClassProtectedMethodPDParam} {\em (hash)\/}. A parameter documented by this documentation block. \begin{itemize}
\item name =$>$ {\bf ClassProtectedMethodPDParamName} {\em (string)\/}. Name of the parameter. \end{itemize}
\end{itemize}
\item doc =$>$ {\bf ClassProtectedMethodPDDoc} {\em (doc)\/}. Documentation for this parameter documentation block. \end{itemize}
\end{itemize}
\item doc =$>$ {\bf ClassProtectedMethodDetailedDoc} {\em (doc)\/}. Detailed documentation for the protected method. \item see =$>$ {\bf ClassProtectedMethodSee} {\em (doc)\/}. \char`\"{}See also\char`\"{} documentation for the protected method. \item return =$>$ {\bf ClassProtectedMethodReturn} {\em (doc)\/}. Documentation about the return value of the protected method. \end{itemize}
\item kind =$>$ {\bf ClassProtectedMethodKind} {\em (string)\/}. Kind of protected method (usually \char`\"{}function\char`\"{}). \item name =$>$ {\bf ClassProtectedMethodName} {\em (string)\/}. Name of the protected method. \item type =$>$ {\bf ClassProtectedMethodType} {\em (string)\/}. Data type returned by the protected method. \item static =$>$ {\bf ClassProtectedMethodStatic} {\em (string)\/}. Whether the protected method is static. \end{itemize}
\end{itemize}
\end{itemize}
\item public\_\-typedefs =$>$ {\bf ClassPublicTypedefs} {\em (hash)\/}. Information about the public typedefs in the class. \begin{itemize}
\item members =$>$ {\bf ClassPublicTypedefList} {\em (list)\/}. public typedef list. \begin{itemize}
\item {\bf ClassPublicTypedef} {\em (hash)\/}. A public typedef. \begin{itemize}
\item protection =$>$ {\bf ClassPublicTypedefProtection} {\em (string)\/}. Protection of the public typedef. \item detailed =$>$ {\bf ClassPublicTypedefDetailed} {\em (hash)\/}. Detailed information about the public typedef. \begin{itemize}
\item doc =$>$ {\bf ClassPublicTypedefDetailedDoc} {\em (doc)\/}. Detailed documentation for the public typedef. \item see =$>$ {\bf ClassPublicTypedefSee} {\em (doc)\/}. \char`\"{}See also\char`\"{} documentation for the public typedef. \end{itemize}
\item kind =$>$ {\bf ClassPublicTypedefKind} {\em (string)\/}. Kind of public typedef (usually \char`\"{}typedef\char`\"{}). \item name =$>$ {\bf ClassPublicTypedefName} {\em (string)\/}. Name of the public typedef. \item type =$>$ {\bf ClassPublicTypedefType} {\em (string)\/}. Data type of the public typedef. \end{itemize}
\end{itemize}
\end{itemize}
\item public\_\-members =$>$ {\bf ClassPublicMembers} {\em (hash)\/}. Information about the public members in the class. \begin{itemize}
\item members =$>$ {\bf ClassPublicMemberList} {\em (list)\/}. public member list. \begin{itemize}
\item {\bf ClassPublicMember} {\em (hash)\/}. A public member. \begin{itemize}
\item protection =$>$ {\bf ClassPublicMemberProtection} {\em (string)\/}. Protection of the public member. \item detailed =$>$ {\bf ClassPublicMemberDetailed} {\em (hash)\/}. Detailed information about the public member. \begin{itemize}
\item doc =$>$ {\bf ClassPublicMemberDetailedDoc} {\em (doc)\/}. Detailed documentation for the public member. \item see =$>$ {\bf ClassPublicMemberSee} {\em (doc)\/}. \char`\"{}See also\char`\"{} documentation for the public member. \end{itemize}
\item kind =$>$ {\bf ClassPublicMemberKind} {\em (string)\/}. Kind of public member (usually \char`\"{}variable\char`\"{}). \item name =$>$ {\bf ClassPublicMemberName} {\em (string)\/}. Name of the public member. \item type =$>$ {\bf ClassPublicMemberType} {\em (string)\/}. Data type of the public member. \end{itemize}
\end{itemize}
\end{itemize}
\item private\_\-methods =$>$ {\bf ClassPrivateMethods} {\em (hash)\/}. Information about the private methods in the class. \begin{itemize}
\item members =$>$ {\bf ClassPrivateMethodList} {\em (list)\/}. private method list. \begin{itemize}
\item {\bf ClassPrivateMethod} {\em (hash)\/}. A private method. \begin{itemize}
\item parameters =$>$ {\bf ClassPrivateMethodParams} {\em (list)\/}. List of the parameters of the private method. \begin{itemize}
\item {\bf ClassPrivateMethodParam} {\em (hash)\/}. A parameter of the private method. \begin{itemize}
\item declaration\_\-name =$>$ {\bf ClassPrivateMethodParamName} {\em (string)\/}. The name of the parameter. \item type =$>$ {\bf ClassPrivateMethodParamType} {\em (string)\/}. The data type of the parameter. \end{itemize}
\end{itemize}
\item protection =$>$ {\bf ClassPrivateMethodProtection} {\em (string)\/}. Protection of the private method. \item virtualness =$>$ {\bf ClassPrivateMethodVirtualness} {\em (string)\/}. Virtualness of the private method. \item detailed =$>$ {\bf ClassPrivateMethodDetailed} {\em (hash)\/}. Detailed information about the private method. \begin{itemize}
\item params =$>$ {\bf ClassPrivateMethodPDBlocks} {\em (list)\/}. List of parameter documentation blocks for the private method. \begin{itemize}
\item {\bf ClassPrivateMethodPDBlock} {\em (hash)\/}. A parameter documentation block for the private method. \begin{itemize}
\item parameters =$>$ {\bf ClassPrivateMethodPDParams} {\em (list)\/}. Parameter list for this parameter documentation block. \begin{itemize}
\item {\bf ClassPrivateMethodPDParam} {\em (hash)\/}. A parameter documented by this documentation block. \begin{itemize}
\item name =$>$ {\bf ClassPrivateMethodPDParamName} {\em (string)\/}. Name of the parameter. \end{itemize}
\end{itemize}
\item doc =$>$ {\bf ClassPrivateMethodPDDoc} {\em (doc)\/}. Documentation for this parameter documentation block. \end{itemize}
\end{itemize}
\item doc =$>$ {\bf ClassPrivateMethodDetailedDoc} {\em (doc)\/}. Detailed documentation for the private method. \item see =$>$ {\bf ClassPrivateMethodSee} {\em (doc)\/}. \char`\"{}See also\char`\"{} documentation for the private method. \item return =$>$ {\bf ClassPrivateMethodReturn} {\em (doc)\/}. Documentation about the return value of the private method. \end{itemize}
\item kind =$>$ {\bf ClassPrivateMethodKind} {\em (string)\/}. Kind of private method (usually \char`\"{}function\char`\"{}). \item name =$>$ {\bf ClassPrivateMethodName} {\em (string)\/}. Name of the private method. \item type =$>$ {\bf ClassPrivateMethodType} {\em (string)\/}. Data type returned by the private method. \item static =$>$ {\bf ClassPrivateMethodStatic} {\em (string)\/}. Whether the private method is static. \end{itemize}
\end{itemize}
\end{itemize}
\item public\_\-methods =$>$ {\bf ClassPublicMethods} {\em (hash)\/}. Information about the public methods in the class. \begin{itemize}
\item members =$>$ {\bf ClassPublicMethodList} {\em (list)\/}. public method list. \begin{itemize}
\item {\bf ClassPublicMethod} {\em (hash)\/}. A public method. \begin{itemize}
\item parameters =$>$ {\bf ClassPublicMethodParams} {\em (list)\/}. List of the parameters of the public method. \begin{itemize}
\item {\bf ClassPublicMethodParam} {\em (hash)\/}. A parameter of the public method. \begin{itemize}
\item declaration\_\-name =$>$ {\bf ClassPublicMethodParamName} {\em (string)\/}. The name of the parameter. \item type =$>$ {\bf ClassPublicMethodParamType} {\em (string)\/}. The data type of the parameter. \end{itemize}
\end{itemize}
\item protection =$>$ {\bf ClassPublicMethodProtection} {\em (string)\/}. Protection of the public method. \item virtualness =$>$ {\bf ClassPublicMethodVirtualness} {\em (string)\/}. Virtualness of the public method. \item detailed =$>$ {\bf ClassPublicMethodDetailed} {\em (hash)\/}. Detailed information about the public method. \begin{itemize}
\item params =$>$ {\bf ClassPublicMethodPDBlocks} {\em (list)\/}. List of parameter documentation blocks for the public method. \begin{itemize}
\item {\bf ClassPublicMethodPDBlock} {\em (hash)\/}. A parameter documentation block for the public method. \begin{itemize}
\item parameters =$>$ {\bf ClassPublicMethodPDParams} {\em (list)\/}. Parameter list for this parameter documentation block. \begin{itemize}
\item {\bf ClassPublicMethodPDParam} {\em (hash)\/}. A parameter documented by this documentation block. \begin{itemize}
\item name =$>$ {\bf ClassPublicMethodPDParamName} {\em (string)\/}. Name of the parameter. \end{itemize}
\end{itemize}
\item doc =$>$ {\bf ClassPublicMethodPDDoc} {\em (doc)\/}. Documentation for this parameter documentation block. \end{itemize}
\end{itemize}
\item doc =$>$ {\bf ClassPublicMethodDetailedDoc} {\em (doc)\/}. Detailed documentation for the public method. \item see =$>$ {\bf ClassPublicMethodSee} {\em (doc)\/}. \char`\"{}See also\char`\"{} documentation for the public method. \item return =$>$ {\bf ClassPublicMethodReturn} {\em (doc)\/}. Documentation about the return value of the public method. \end{itemize}
\item kind =$>$ {\bf ClassPublicMethodKind} {\em (string)\/}. Kind of public method (usually \char`\"{}function\char`\"{}). \item name =$>$ {\bf ClassPublicMethodName} {\em (string)\/}. Name of the public method. \item type =$>$ {\bf ClassPublicMethodType} {\em (string)\/}. Data type returned by the public method. \item static =$>$ {\bf ClassPublicMethodStatic} {\em (string)\/}. Whether the public method is static. \end{itemize}
\end{itemize}
\end{itemize}
\end{itemize}
\end{itemize}
\item files =$>$ {\bf Files} {\em (list)\/}. Documented files. \begin{itemize}
\item {\bf File} {\em (hash)\/}. A documented file. \begin{itemize}
\item detailed =$>$ {\bf FileDetailed} {\em (hash)\/}. Detailed information about the file. \begin{itemize}
\item doc =$>$ {\bf FileDetailedDoc} {\em (doc)\/}. Detailed documentation block for the file. \end{itemize}
\item functions =$>$ {\bf FileFunctions} {\em (hash)\/}. Information about the functions in the file. \begin{itemize}
\item members =$>$ {\bf FileFunctionList} {\em (list)\/}. function list. \begin{itemize}
\item {\bf FileFunction} {\em (hash)\/}. A function. \begin{itemize}
\item parameters =$>$ {\bf FileFunctionParams} {\em (list)\/}. List of the parameters of the function. \begin{itemize}
\item {\bf FileFunctionParam} {\em (hash)\/}. A parameter of the function. \begin{itemize}
\item declaration\_\-name =$>$ {\bf FileFunctionParamName} {\em (string)\/}. The name of the parameter. \item type =$>$ {\bf FileFunctionParamType} {\em (string)\/}. The data type of the parameter. \end{itemize}
\end{itemize}
\item protection =$>$ {\bf FileFunctionProtection} {\em (string)\/}. Protection of the function. \item virtualness =$>$ {\bf FileFunctionVirtualness} {\em (string)\/}. Virtualness of the function. \item detailed =$>$ {\bf FileFunctionDetailed} {\em (hash)\/}. Detailed information about the function. \begin{itemize}
\item params =$>$ {\bf FileFunctionPDBlocks} {\em (list)\/}. List of parameter documentation blocks for the function. \begin{itemize}
\item {\bf FileFunctionPDBlock} {\em (hash)\/}. A parameter documentation block for the function. \begin{itemize}
\item parameters =$>$ {\bf FileFunctionPDParams} {\em (list)\/}. Parameter list for this parameter documentation block. \begin{itemize}
\item {\bf FileFunctionPDParam} {\em (hash)\/}. A parameter documented by this documentation block. \begin{itemize}
\item name =$>$ {\bf FileFunctionPDParamName} {\em (string)\/}. Name of the parameter. \end{itemize}
\end{itemize}
\item doc =$>$ {\bf FileFunctionPDDoc} {\em (doc)\/}. Documentation for this parameter documentation block. \end{itemize}
\end{itemize}
\item doc =$>$ {\bf FileFunctionDetailedDoc} {\em (doc)\/}. Detailed documentation for the function. \item see =$>$ {\bf FileFunctionSee} {\em (doc)\/}. \char`\"{}See also\char`\"{} documentation for the function. \item return =$>$ {\bf FileFunctionReturn} {\em (doc)\/}. Documentation about the return value of the function. \end{itemize}
\item kind =$>$ {\bf FileFunctionKind} {\em (string)\/}. Kind of function (usually \char`\"{}function\char`\"{}). \item name =$>$ {\bf FileFunctionName} {\em (string)\/}. Name of the function. \item type =$>$ {\bf FileFunctionType} {\em (string)\/}. Data type returned by the function. \item static =$>$ {\bf FileFunctionStatic} {\em (string)\/}. Whether the function is static. \end{itemize}
\end{itemize}
\end{itemize}
\item name =$>$ {\bf FileName} {\em (string)\/}. Name of the file. \item variables =$>$ {\bf FileVariables} {\em (hash)\/}. Information about the variables in the file. \begin{itemize}
\item members =$>$ {\bf FileVariableList} {\em (list)\/}. variable list. \begin{itemize}
\item {\bf FileVariable} {\em (hash)\/}. A variable. \begin{itemize}
\item protection =$>$ {\bf FileVariableProtection} {\em (string)\/}. Protection of the variable. \item detailed =$>$ {\bf FileVariableDetailed} {\em (hash)\/}. Detailed information about the variable. \begin{itemize}
\item doc =$>$ {\bf FileVariableDetailedDoc} {\em (doc)\/}. Detailed documentation for the variable. \item see =$>$ {\bf FileVariableSee} {\em (doc)\/}. \char`\"{}See also\char`\"{} documentation for the variable. \end{itemize}
\item kind =$>$ {\bf FileVariableKind} {\em (string)\/}. Kind of variable (usually \char`\"{}variable\char`\"{}). \item name =$>$ {\bf FileVariableName} {\em (string)\/}. Name of the variable. \item type =$>$ {\bf FileVariableType} {\em (string)\/}. Data type of the variable. \end{itemize}
\end{itemize}
\end{itemize}
\item typedefs =$>$ {\bf FileTypedefs} {\em (hash)\/}. Information about the typedefs in the file. \begin{itemize}
\item members =$>$ {\bf FileTypedefList} {\em (list)\/}. typedef list. \begin{itemize}
\item {\bf FileTypedef} {\em (hash)\/}. A typedef. \begin{itemize}
\item protection =$>$ {\bf FileTypedefProtection} {\em (string)\/}. Protection of the typedef. \item detailed =$>$ {\bf FileTypedefDetailed} {\em (hash)\/}. Detailed information about the typedef. \begin{itemize}
\item doc =$>$ {\bf FileTypedefDetailedDoc} {\em (doc)\/}. Detailed documentation for the typedef. \item see =$>$ {\bf FileTypedefSee} {\em (doc)\/}. \char`\"{}See also\char`\"{} documentation for the typedef. \end{itemize}
\item kind =$>$ {\bf FileTypedefKind} {\em (string)\/}. Kind of typedef (usually \char`\"{}typedef\char`\"{}). \item name =$>$ {\bf FileTypedefName} {\em (string)\/}. Name of the typedef. \item type =$>$ {\bf FileTypedefType} {\em (string)\/}. Data type of the typedef. \end{itemize}
\end{itemize}
\end{itemize}
\end{itemize}
\end{itemize}
\end{itemize}
\end{itemize}
